---
title: "MATH1115 PROJECT 1"
author: "SID:520477256 "
subtitle: "Project 1"
date: "University of Sydney | MATH1115 | August 2024"
output:
  html_document:
    code_download: true # embed .Rmd file
    toc: true  # table of contents
    toc_depth: 3
    toc_float: true # toc is always visible when scrolled
    number_sections: false 
    df_print: paged # format data frame outputs automatically
    theme: sandstone # theme the doc
    highlight: tango # theme syntax colouring
---

```{css newstyles, echo=FALSE}
body {
  color: black;
}
```

# Executive Summary
- The aim of this report is to ...
- The main discoveries are ...

# Full Report

## Initial Data Analysis (IDA)


Summary (suggesstion):

- The data came from ...
- The data is/is not valid because ...
- Possible issues include ...
- Each row represents ...
- Each column represents ...

```{r}
# Read dataset
data <- read.csv("~/Desktop/MATH1115/Labs/data/Sleep_health_and_lifestyle_dataset.csv")
library(tidyverse)
```

```{r}
# Show classification of variables
str(data)
```


## Research Question 1

Insert text and analysis. 




## Research Question 2

Insert text and analysis. 

## Research Question 3

## Research Question 4

# References

> Style: APA 

